### 2015-05-08 fundamentals/intro.tex
Reviewer 1: IA: would be good to mention that such simulators can be used both for questions addressing operational facets of nuclear energy systems, e.g. interim UNF storage optimisation,as well as 'strategic' questions allowing to address R&D-options assessment.

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options. The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the dynamics of transitions
between fuel cycles, and many other measures of performance can be expressed in
terms of these metrics. For example, economic feasibility is often measured in
\gls{LCOE}, requiring calculation of lifetime
fuel costs and electricity generation, while environmental performance might be
measured by spent fuel volume, toxicity, or mined uranium.  A meta-analysis of
fuel cycle systems studies identified over two dozen unique quantitative
metrics spanning economics and cost, environmental sustainability and waste
management impacts, safety, security and nonproliferation, resource adequacy
and utilization, among others \cite{flicker_evaluation_2014}. With few 
exceptions (e.g.  \cite{poinssot_assessment_2014}), these metrics are derived 
from mass balances calculated by a fuel cycle simulator.

>>>>

Nuclear fuel cycle simulators drive \gls{RDD} by calculating `metrics',
quantitative measures of performance that can be compared among fuel cycle
options.  The feasibility of the technology development and deployment
strategies which comprise a fuel cycle option, the operational features of
nuclear energy systems, the dynamics of transitions between fuel cycles, and
many other measures of performance can be expressed in terms of these metrics.
For example, economic feasibility is often measured in \gls{LCOE}, requiring
calculation of lifetime fuel costs and electricity generation, while
environmental performance might be measured by spent fuel volume, toxicity, or
mined uranium.  A meta-analysis of fuel cycle systems studies identified over
two dozen unique quantitative metrics spanning economics and cost,
environmental sustainability and waste management impacts, safety, security and
nonproliferation, resource adequacy and utilization, among others
\cite{flicker_evaluation_2014}. With few exceptions (e.g.
\cite{poinssot_assessment_2014}), these metrics are derived from mass balances
calculated by a fuel cycle simulator.
